### 2010-12-06 report/report.tex
few spelling changes

We evaluated the efficacy of a set of parameters by sending these
parameters to the robot and instructing it to walk for a certain length
of time. The robot always begins from the same position and returns to the
starting position at the end of the run in order to allow for uniformity
in measuring. More efficient parameters resulted in a faster gait, which
translated into a longer distance walked and a better score. After completing
an evluation, the robot sent the resulting distance walked back to the
host computer and prepared itself for a new set of parameters to evaluate.

Each algorithm was run on 3 different initial parameter vectors on the
physical robot. We decided to evaluate all methods starting at the
same three vector in order to allow for the fair comparison of each
algorihtm.  We evaluate
each method based on the amount of improvement seen from the initial
parameter vectors, and on the fastest speeds achieved during runs.

@@

\editbox{Pull out vectors A, B, and C into separte bulletted list, and
  make table, like below}

\begin{tabular}{|r|c|c|c|}
\hline
                                         & A       & B      & C      \\
\hline
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   \\
\hline
Guassian Random Hill Climbing            & 3.10    & 13.59  & 13.40  \\
\hline
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   \\
\hline
Random                                   & 6.04    & 17.26  & 4.90   \\
\hline
Simplex (Nelder-Mead)                    & 8.51    & 13.62  & 14.83  \\
\hline
Linear Regression                        & 27.58   & 12.51  & 1.95   \\
\hline
SVM Regression                           & ???     & ???    & ???    \\
\hline
Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???    \\
\hline
\end{tabular}

@@

\section{Acknowledgments}
% List any people not on the team who helped you with your project: Your
% TA, other people you consulted with or had useful discussions (say in 
% a word or two what they did), people who proofread your report, and 
% any external code you used (libraries etc).
\begin{itemize}
\item Hod Lipson, Cornell Computational Synthesis Lab: advisor
\item Jim T\o rreson, University of Oslo: advisor
\item Juan Zagal, University of Chile: designed and printed robot and provided assistance
\item Jeff Clune, CCSL Red Couch: collaborated on HyperNEAT implementation/testing
\item Cooper Bills, Cornell University: assisted with Wii tracker development
\item Anshumali Srivastava, Cornell University: Teaching Assistant
\end{itemize}

@@

>>>>

We evaluated the efficacy of a set of parameters by sending these
parameters to the robot and instructing it to walk for a certain length
of time. The robot always begins from the same position and returns to the
starting position at the end of the run in order to allow for uniformity
in measuring. More efficient parameters resulted in a faster gait, which
translated into a longer distance walked and a better score. After completing
an evaluation, the robot sent the resulting distance walked back to the
host computer and prepared itself for a new set of parameters to evaluate.

Each algorithm was run on 3 different initial parameter vectors on the
physical robot. We decided to evaluate all methods starting at the
same three vector in order to allow for the fair comparison of each
algorithm.  We evaluate
each method based on the amount of improvement seen from the initial
parameter vectors, and on the fastest speeds achieved during runs.

@@

\editbox{Pull out vectors A, B, and C into separate bulletted list, and
  make table, like below}

\begin{tabular}{|r|c|c|c|}
\hline
                                         & A       & B      & C      \\
\hline
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   \\
\hline
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  \\
\hline
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   \\
\hline
Random                                   & 6.04    & 17.26  & 4.90   \\
\hline
Simplex (Nelder-Mead)                    & 8.51    & 13.62  & 14.83  \\
\hline
Linear Regression                        & 27.58   & 12.51  & 1.95   \\
\hline
SVM Regression                           & ???     & ???    & ???    \\
\hline
Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???    \\
\hline
\end{tabular}

@@

\section{Acknowledgments}
% List any people not on the team who helped you with your project: Your
% TA, other people you consulted with or had useful discussions (say in 
% a word or two what they did), people who proofread your report, and 
% any external code you used (libraries etc).
\begin{itemize}
\item Hod Lipson, Cornell Computational Synthesis Lab: adviser
\item Jim T\orreson, University of Oslo: adviser
\item Juan Zagal, University of Chile: designed and printed robot and provided assistance
\item Jeff Clune, CCSL Red Couch: collaborated on HyperNEAT implementation/testing
\item Cooper Bills, Cornell University: assisted with Wii tracker development
\item Anshumali Srivastava, Cornell University: Teaching Assistant
\end{itemize}

@@

% LocalWords:  vertices
